### 2023-11-13 sections/2-methods.tex
better presentation of repeated rnn complexity
fixing inaccuracy

To determine the asymptotic complexity of fine search, we must estimate $|F|$, the number of clusters for which we must look at all of the cluster's points.
With $\rho$-NN search, $F$ is the union of clusters which are within a distance of $r + \hat{r_c}$ from the query, where $r$ is the search radius, and $\hat{r_c}$ is the mean radius of leaf clusters, as in \cite{yu2015entropy}.
With $k$-NN by Repeated $\rho$-NN, however, the value of $r$ is dependent on the distance to the $k$th nearest neighbor, which is query-dependent.
Thus, for $k$-NN by Repeated $\rho$-NN, we adjust the definition of $F$ to be the union of clusters which are within a distance of $r' + \hat{r_c}$ from the query, where $r'$ is the distance to the $k$th nearest neighbor and $\hat{r_c}$ is defined as before.

@@

\begin{equation*}
    |F| \leq \gamma |B(q, r')|\left(1+ \frac{2\hat{r_c}}{r'}\right)^d
\end{equation*}

@@

\begin{equation}
    |F| \leq \gamma k\left(1+ \frac{2\hat{r_c}}{r'}\right)^d
    \label{eq:methods:knn-by-rnn-fine-search}
\end{equation}

@@

\begin{equation}
    \mathcal{O}\left(\log_2{\mathcal{N}_{\hat{r_c}}(X)} + k\left(\frac{2\hat{r_c}}{\hat{r}}\right)^d\left(\frac{k}{\hat{C}}\right)^{\frac{-d}{\hat{d}}}\right)
    \label{eq:methods:knn-by-rnn-complexity}
\end{equation}

>>>>

To determine the asymptotic complexity of fine search, we must estimate $|H|$, the expected number of hits we examine.
With $\rho$-NN search, $H$ is the union of clusters which are within a distance of $r + \hat{r_c}$ from the query, where $r$ is the search radius, and $\hat{r_c}$ is the mean radius of leaf clusters, as in \cite{yu2015entropy}.
With $k$-NN by Repeated $\rho$-NN, however, the value of $r$ is dependent on the distance to the $k$th nearest neighbor, which is query-dependent.
Thus, for $k$-NN by Repeated $\rho$-NN, we adjust the definition of $H$ to be the union of clusters which are within a distance of $r' + \hat{r_c}$ from the query, where $r'$ is the distance to the $k$th nearest neighbor and $\hat{r_c}$ is defined as before.

@@

\begin{equation*}
    |H| \leq \gamma |B(q, r')|\left(1+ \frac{2\hat{r_c}}{r'}\right)^d
\end{equation*}

@@

\begin{equation}
    |H| \leq \gamma k\left(1+ \frac{2\hat{r_c}}{r'}\right)^d
    \label{eq:methods:knn-by-rnn-fine-search}
\end{equation}

@@

\begin{gather}
    \mathcal{O}\Bigg(
    \underbrace{\log_2{\mathcal{N}_{\hat{r_c}}(X)}}_{\textrm{metric entropy}} + 
    \overbrace{k}^{\textrm{output size}}
    \underbrace{\left(\frac{2\hat{r_c}}{\hat{r}}\right)^d\left(\frac{k}{\hat{C}}\right)^{\frac{-d}{\hat{d}}}}_{\textrm{scaling factor}}\Bigg)
    \label{eq:methods:knn-by-rnn-complexity}
\end{gather}
